---
title: "COVID_hypothesis_testing"
author: "Matthew Miller"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
```


Read the hospital data
```{r}
hospital_data <- read_csv("data/Hospitals_gdb_771050112109123987.csv")
```
Read the COVID-19 data
```{r}
covid_data <- read_csv("data/total_cases_by_county.csv")
```
Preprocess hospital data and hospital data, ensuring the join column is the same data type
```{r}
hospital_density <- hospital_data %>%
  count(COUNTYFIPS, name = "hospital_count")

covid_data <- covid_data %>%
  mutate(COUNTYFIPS = as.character(COUNTYFIPS))

hospital_density <- hospital_density %>%
  mutate(COUNTYFIPS = as.character(COUNTYFIPS))
```
Join by county (using FIPS code)
```{r}
combined_data <- covid_data %>%
  inner_join(hospital_density, by = "COUNTYFIPS")
```

Visualize the data
```{r}
ggplot(combined_data, aes(x = hospital_count, y = total_cases)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "COVID-19 Cases vs Hospital Density",
       x = "Hospitals per County",
       y = "Total COVID-19 Cases")
```

Test hypothesis
```{r}
model <- lm(total_cases ~ hospital_count, data = combined_data)
summary(model)
confint(model)
```

This p-value of less than 2.2e-16 falls outside of our confidence interval of 2.5-97.5%, indicating that we should reject the null hypothesis and accept the alternative hypothesis. That is, the data indicates a relationship between hospital density and total number of COVID-19 cases in 2020.